A game-theory modeling approach to utility and strength of interactions dynamics in biomedical research social networks

### 2017-03-30 casm.tex
Added new references as requested by reviewer 1.Fixed reference Li and Cao in the .bib file. Also, marked in red additions and modifications to the text.

The strength of the interaction, represented by $w$, is a property of the link between two agents and
gets updated according to an $A_{ij}$ matrix of a coordination game. In the $w$ matrix, the highest value
goes to an edge when both agents cooperate, getting an $R$ for reward; if one of
them defects, the connection gets weaker getting $P$ for the collaborative
connection being punished. If both agents defect, the value $w$ doesn't change,
which means that agents didn't interact or that the interaction gets nullified
$N$. In this game, the best action for any agent is to coordinate with its
neighbor, either because it wins or because it doesn't lose. \\

@@

After each game, the agent adds up utility ($u$), which is the sum of the
payoffs following the PD matrix. A pair of neighbors will add or substract from the strength of
their interaction ($w_{ji}$) as they coordinate or not, being $w$
also cumulative. We measure global utility and strength of interaction for the whole
network. Global utility $U$ is the sum of all individual utilities and global
strength of interaction or $W$ is the sum of every pair of agents' links
$w$. Strength of interaction may have different meanings. From an empirical point of view, it simply means the number of times two researchers have collaborated together in a comon research project. From a sociological and qualitative point of view, if these two scientists have been willing to collaborate more than once, it may signify some form of "trust" among them. But this may not be the only possible interpreation since it can be different for each case. Since the strength of interactions can be sociologically interpreted in so many ways, we decided to just quantify the  times two researchers collaborate, and by doing this avoiding any generalized interpretation of the quality of the interactions among researchers. \\

@@

The probability for an agent to cooperate or defect depends on a
number ($\eta$) that refers to a historical balance between average
utility and the average strength of the connections with its
neighbors. It is modeled so because we assume that whatever the result
in utility or strength of interaction, as long as one of them
increases, the player will be confident in the strategy followed so
far. In every simulation step, each agent will independently play both games with
every neighbor. Nonetheless, the agent sets its decision to cooperate or defect beforehand
by assessing the overall situation of its relationships. This may
sound odd, since one may think that a person decides for each
relationship separately. However in this way players are optimizing
access to resources and the strength of interactions to their
neighbors at the same time, since their state is set by
considering both together. The strength of interaction is updated independently for each pair of agents.  In a single play some interactions might be weakened, some may get strengthened and others may remain unaffected. Moreover, in this model, history is kept in the network as strength of interactions and it conditions the agent\'s disposition to cooperate or to defect. As the sayings go: Burnt children dread fire; A bad dog is not born but made.\\

@@

$\eta_i = \frac{\langle f_i \rangle + \langle w_{ij} \rangle _j}{2}$\\

>>>>

The strength of the interaction, represented by $w$, is a property of the link between two agents and
gets updated according to the payoff matrix of a coordination game. In the $w$ matrix, the highest value
goes to an edge when both agents cooperate, getting an $R$ for reward; if one of
them defects, the connection gets weaker getting $P$ for the collaborative
connection being punished. If both agents defect, the value $w$ doesn't change,
which means that agents didn't interact or that the interaction gets nullified
$N$. In this game, the best action for any agent is to coordinate with its
neighbor, either because it wins or because it doesn't lose. \\

@@

After each game, the agent adds up utility ($u$), which is the sum of the
payoffs following the PD matrix. A pair of neighbors will add or substract from
the strength of their interaction ($w_{ji}$) as they coordinate or not, being
$w$ also cumulative. We measure global utility and strength of interaction for
the whole network. Global utility $U$ is the sum of all individual utilities and
global strength of interaction or $W$ is the sum of every pair of agents' links
$w$. {\color{red}Strength of interaction may have different meanings. From an empirical
point of view, it simply means the number of times two researchers have
collaborated together in a common research project. From a sociological and
qualitative point of view, if these two scientists have been willing to
collaborate more than once, it may signify some form of ``loyalty'' among them. But
this may not be the only possible interpreation since it can be different for
each case. Since the strength of interactions can be sociologically interpreted
in so many ways, we decided to just quantify the  times two researchers
collaborate, and by doing this avoiding any generalized interpretation of the
quality of the interactions among researchers.} \\

@@

The probability for an agent to cooperate or defect depends on a number ($\eta$)
that refers to a historical balance between average utility and the average
strength of the connections with its neighbors. It is modeled so because we
assume that whatever the result in utility or strength of interaction, as long
as one of them increases, the player will be confident in the strategy followed
so far. {\color{red}In every simulation step, each agent will independently play both games
with every neighbor. Nonetheless, the agent sets its decision to cooperate or
defect beforehand by assessing the overall situation of its relationships. This
may sound odd, since one may think that a person decides for each relationship
separately. However in this way players are optimizing access to resources and
the strength of interactions to their neighbors at the same time, since their
state is set by considering both together. The strength of interaction is
updated independently for each pair of agents.  In a single play some
interactions might be weakened, some may get strengthened and others may remain
unaffected. Moreover, in this model, history is kept in the network as strength
of interactions and it conditions the agent\'s disposition to cooperate or to
defect. As the sayings go: Burnt children dread fire; A bad dog is not born but made.}\\

@@

$\eta_i = \frac{\langle u_i \rangle + \langle w_{ij} \rangle _j}{2}$\\
